Apparent preferences for cognitive effort fade when multiple forms of effort

### 2021-05-30 Manuscript.Rmd
almost done with fig captions

```{r Task Plot (Fig. 1), eval = !figsEnd, out.width = "80%", fig.align = "center", fig.cap= "Task design and optimal behavior. A: General foraging trial structure. On each trial, participants were offered to earn money by sustaining effort or waiting during the handling time (2, 10, or 14 s). The end of a trial was followed by a travel time (handling and travel times always added up to 16 s). Participants could skip unfavorable trials and immediately start traveling to a potentially better offer. In Experiment 1, cost was fixed per participant and handling time varied per block. In Experiment 2, handling time was fixed at 10 s, but a combination of effort and delay trials changed per block. B: Possible earnings per second for each acceptance threshold (i.e. the smallest amount accepted) for each handling time. Circles denote the reward-maximizing threshold for each block, which is described in the table. Experiments shared the 10 s handling block, in which it was optimal to skip all 4 cent offers."}

@@

```{r General prop & earnings plots (Fig. 2), eval = !figsEnd, fig.width = 10, fig.height = 4, fig.align = "center", fig.cap = "Overall choice behavior in Experiment 1. Left: Proportion accepted per cost. Middle: Total number of dollars earned by each group by the end of the experiment. Right: The relationship between proportion accepted and total earned. Consistent with the foraging design, participants who over and under accepted earned the least. These figures suggest that people are willing to pursue cognitively effortful actions at the expense of earnings."}
# plots generated in 16.2.1. and 16.1.3.
#(propPlot <- prop1 | earnings1 | earnFitplot_btw)
#ggsave("./Images/FIG2_props.png", propPlot, device = "png", height = 4, width = 10)

@@

```{r mixed effects plots (Fig. 3), eval = !figsEnd, out.width = "80%", fig.align = "center", fig.cap = "Comparing acceptance rates among costs for each reward and handling combination. A: Proportion accepted by each group for every combination of handling time and reward. Grey dots indicate the reward-maximizing acceptance for each combination. B: Matrix portraying the coefficients (color scale) and significance that resulted from switching the reference cost condition (crosses mark non-significant comparisons). Each entry shows how much more likely a group was to accept compared to the reference condition (row). C: AIC and BIC values for a mixed-effects model comparison, ranging from a base intercept-only to a full-interaction model. Both metrics yielded the same values across models."}
#hrPlot_btw / (ABIC_plot_btw | ME_matrix_btw) # doesn't work with corrplot.. oh well
include_graphics("./Images/FIG3_btwlogistic.png")
```

@@

```{r Survival and prepost plots (Fig. 4), eval = !figsEnd, fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "Choice consistency and stability in Experiment 1. A: Survival curve showing quit times within trial. B: Distribution of times when participants quit a trial over time. C: Proportion accepted in the second half as a function of first half acceptances. Dashed lines indicate the mean for each group. D: proportion accepted over time per group."}
# individual plots generated in 16.3.1. and 16.3.2.
# to recreate the combined plot and save it:
# historyPlot_btw <- (suppressWarnings(survPlot_btw) | RTplot_btw) / (prepost_btw$scatterplot | prepost_btw$propBlocks) + 
#   plot_annotation(tag_levels = 'A') & 
#   theme(plot.tag = element_text(size = 20, face = "bold"))
# ggsave("./Images/FIG4_survivalbtw.png", historyPlot_btw, device = "png", height = 8, width = 10)
include_graphics("./Images/FIG4_survivalbtw.png")
```

@@

```{r Prepost mixed effects plot (Fig. 5), eval = !figsEnd, fig.align = "center", fig.cap = "Acceptance behavior over time in Experiment 1. A: Proportion of acceptances per handling, reward, and session half, showing that effortful demands were less frequently accepted over time. B: Mixed-effects coefficients denoting the comparison among costs acceptances for each half separately (mirrored along the diagonal). Even though acceptances steadily decreased in the effort groups, the relative preferences were preserved."}
# left plot in 16.3.2
# ggsave("./Images/prepost_btw.png", hrprepostPlot_btw, device = "png", height = 6, width = 6)
include_graphics("./Images/FIG5_prepostbtw.png")

@@

```{r Earnings/prop completed/ME plots (Fig. 6), eval = !figsEnd, fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "Within-subjects acceptance behavior. A: Quadratic relationship between trial completions and total earnings. B: proportion of acceptances of each reward per cost condition. C: Matrix of mixed-effects coefficients showing comparisons among costs (while controlling for reward amount). Comparisons between effort and wait trials from different blocks are omitted, as these are not considered in our original predictions. Crosses mark non-significant comparisons. D: AIC and BIC values for models of increasing complexity (a priori = AllMain)."}
# earnFitplot_wth, hrPlot_wth, mixLogis_compare_wth$plot
#ggsave("./Images/aic_wth.png", mixLogis_compare_wth$plot, device = "png", height = 5, width = 5)
include_graphics("./Images/FIG6_wthlogistic.png")
```

@@

```{r Survival and prepost plots (Fig. 7), eval = !figsEnd, fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "Choice consistency and stability in Experiment 2. Top: Survival curve (left), and distribution of quitting times over time (right). Bottom: Proportion accepted in the second half as a function of first half acceptances (left). Dashed lines indicate the mean for each cost. On the right, the proportion accepted every time participants experienced a given block type."}
# plots generated in 16.3.1. and 16.3.3.
# historyPlot_wth <- (suppressWarnings(survPlot_wth) | suppressWarnings(RTplot_wth)) / (prepost_wth$scatterplot | prepost_wth$propBlocks) + 
#     plot_annotation(tag_levels = 'A') &
#     theme(plot.tag = element_text(size = 20, face = "bold"))
#ggsave("./Images/FIG7_survivalwth.png", historyPlot_wth, device = "png", height = 8, width = 10)
include_graphics("./Images/FIG7_survivalwth.png")
```

@@

```{r Prepost mixed effects plots (Fig. 8), eval = !figsEnd, fig.align = "center", fig.cap = "Acceptance rates over time in Experiment 2. Top-Left: Proportion accepted in the first two and last two blocks of the experiment. An initial preference for cognitive effort trials fades amid a global decrease in acceptance rates. Top-Right: Mixed effects coefficient matrix for each half separately. The pattern from the first half resembles what was observed in Experiment 1 (Figure 3). Bottom: Block order effects show attenuated differences for those who started with the physical configuration."}
# hrprepostPlot_wth, blockOrder_wth
# ggsave("./Images/prepostwth_2.png", hrprepostPlot_wth, device = "png", height = 4, width = 8)
include_graphics("./Images/FIG8_prepostwth.png")

@@

```{r BIC and parameter comparison (Fig. 9), eval = !figsEnd, fig.align = "center", fig.height = 5, fig.width = 7, fig.cap = "Computational modeling. A: BIC values for four plausible models of choice behavior for both experiments. Lower values indicate better fit. B: Differences in cost biases produced by each demand. Negative values suggest the Cognitive group acted as if it perceived its demand as valuable. C: Parameter comparison portrays consistent foraging behavior across experiments. D: Behavior recovery of the within-subjects adaptive behavior based on the winning model. The model predictions match the initial preference for cognitive effort, and the eventual convergence of acceptances by the end of the session."}

modelPlot <- (bicPlot + costPlot) / allFitsPlot
ggsave("./Images/FIG9_modelresult_part.png", modelPlot, device = "png", height = 8, width = 11)
include_graphics("./Images/FIG9_modelresults.png")

@@

```{r New Task Plot (Fig. 1), eval = figsEnd, out.width = "80%", fig.align = "center", fig.cap= "Task design and optimal behavior. A: General foraging trial structure. On each trial, participants were offered to earn money by sustaining effort or waiting during the handling time (2, 10, or 14 s). The end of a trial was followed by a travel time (handling and travel times always added up to 16 s). Participants could skip unfavorable trials and immediately start traveling to a potentially better offer. In Experiment 1, cost was fixed per participant and handling time varied per block. In Experiment 2, handling time was fixed at 10 s, but a combination of effort and delay trials changed per block. B: Possible earnings per second for each acceptance threshold (i.e. the smallest amount accepted) for each handling time. Circles denote the reward-maximizing threshold for each block, which is described in the table. Experiments shared the 10 s handling block, in which it was optimal to skip all 4 cent offers."}

@@

```{r New General prop & earnings plots (Fig. 2), eval = figsEnd, fig.width = 10, fig.height = 4, fig.align = "center", fig.cap = "Overall choice behavior in Experiment 1. Left: Proportion accepted per cost. Middle: Total number of dollars earned by each group by the end of the experiment. Right: The relationship between proportion accepted and total earned. Consistent with the foraging design, participants who over and under accepted earned the least. These figures suggest that people are willing to pursue cognitively effortful actions at the expense of earnings."}
# plots generated in 16.2.1. and 16.1.3.
 prop1 | earnings1 | earnFitplot_btw
```

@@

```{r New mixed effects plots (Fig. 3), eval = figsEnd, out.width = "80%", fig.align = "center", fig.cap = "Comparing acceptance rates among costs for each reward and handling combination. A: Proportion accepted by each group for every combination of handling time and reward. Grey dots indicate the reward-maximizing acceptance for each combination. B: Matrix portraying the coefficients (color scale) and significance that resulted from switching the reference cost condition (crosses mark non-significant comparisons). Each entry shows how much more likely a group was to accept compared to the reference condition (row). C: AIC and BIC values for a mixed-effects model comparison, ranging from a base intercept-only to a full-interaction model. Both metrics yielded the same values across models."}
#hrPlot_btw / (ABIC_plot_btw | ME_matrix_btw) # doesn't work with corrplot.. oh well
include_graphics("./Images/FIG3_btwlogistic.png")
```

@@

```{r New Survival and prepost plots (Fig. 4), eval = figsEnd, fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "Choice consistency and stability in Experiment 1. A: Survival curve showing quit times within trial. B: Distribution of times when participants quit a trial over time. C: Proportion accepted in the second half as a function of first half acceptances. Dashed lines indicate the mean for each group. D: proportion accepted over time per group."}
# individual plots generated in 16.3.1. and 16.3.2.
# to recreate the combined plot and save it:
# historyPlot_btw <- (suppressWarnings(survPlot_btw) | RTplot_btw) / (prepost_btw$scatterplot | prepost_btw$propBlocks) + 
#   plot_annotation(tag_levels = 'A') & 
#   theme(plot.tag = element_text(size = 20, face = "bold"))
# ggsave("./Images/FIG4_survivalbtw.png", historyPlot_btw, device = "png", height = 8, width = 10)
include_graphics("./Images/FIG4_survivalbtw.png")
```

@@

```{r New Prepost mixed effects plot (Fig. 5), eval = figsEnd, fig.align = "center", fig.cap = "Acceptance behavior over time in Experiment 1. A: Proportion of acceptances per handling, reward, and session half, showing that effortful demands were less frequently accepted over time. B: Mixed-effects coefficients denoting the comparison among costs acceptances for each half separately (mirrored along the diagonal). Even though acceptances steadily decreased in the effort groups, the relative preferences were preserved."}
include_graphics("./Images/FIG5_prepostbtw.png")
```

@@

```{r New Earnings/prop completed/ME plots (Fig. 6), eval = figsEnd, fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "Within-subjects acceptance behavior. A: Quadratic relationship between trial completions and total earnings. B: proportion of acceptances of each reward per cost condition. C: Matrix of mixed-effects coefficients showing comparisons among costs (while controlling for reward amount). Comparisons between effort and wait trials from different blocks are omitted, as these are not considered in our original predictions. Crosses mark non-significant comparisons. D: AIC and BIC values for models of increasing complexity (a priori = AllMain)."}

include_graphics("./Images/FIG6_wthlogistic.png")
```

@@

```{r New Survival and prepost plots (Fig. 7), eval = figsEnd, fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "Choice consistency and stability in Experiment 2. Top: Survival curve (left), and distribution of quitting times over time (right). Bottom: Proportion accepted in the second half as a function of first half acceptances (left). Dashed lines indicate the mean for each cost. On the right, the proportion accepted every time participants experienced a given block type."}
# plots generated in 16.3.1. and 16.3.3.
(suppressWarnings(survPlot_wth) | suppressWarnings(RTplot_wth)) / (prepost_wth$scatterplot | prepost_wth$propBlocks)
```

@@

```{r New Prepost mixed effects plots (Fig. 8), eval = figsEnd, fig.align = "center", fig.cap = "Acceptance rates over time in Experiment 2. Top-Left: Proportion accepted in the first two and last two blocks of the experiment. An initial preference for cognitive effort trials fades amid a global decrease in acceptance rates. Top-Right: Mixed effects coefficient matrix for each half separately. The pattern from the first half resembles what was observed in Experiment 1 (Figure 3). Bottom: Block order effects show attenuated differences for those who started with the physical configuration."}
include_graphics("./Images/FIG8_prepostwth.png")
```

@@

```{r New BIC and parameter comparison (Fig. 9), eval = figsEnd, fig.align = "center", fig.height = 5, fig.width = 7, fig.cap = "Computational modeling. A: BIC values for four plausible models of choice behavior for both experiments. Lower values indicate better fit. B: Differences in cost biases produced by each demand. Negative values suggest the Cognitive group acted as if it perceived its demand as valuable. C: Parameter comparison portrays consistent foraging behavior across experiments. D: Behavior recovery of the within-subjects adaptive behavior based on the winning model. The model predictions match the initial preference for cognitive effort, and the eventual convergence of acceptances by the end of the session."}

include_graphics("./Images/FIG9_modelresults.png")

#(bicPlot + costPlot) / allFitsPlot
```

>>>>

```{r Task Plot (Fig. 1), eval = !figsEnd, out.width = "80%", fig.align = "center", fig.cap= "Task design and optimal behavior. A: General foraging trial structure. On each trial, participants were offered an opportunity to earn money by sustaining effort or waiting during the handling time (2, 10, or 14 s). The end of a trial was followed by a travel time (handling and travel times always added up to 16 s). Participants could skip unfavorable trials and immediately start traveling to a potentially better offer. In Experiment 1, the type of demand was fixed per participant and handling time varied per block. In Experiment 2, handling time was fixed at 10 s, but a combination of effort and delay trials changed per block. B: Possible earnings per second for each acceptance threshold (i.e. the smallest amount accepted) for each handling time in Experiment 1. Circles denote the reward-maximizing threshold for each block, which is described in the table. Experiment 2 presented only the 10 s handling time, for which it was optimal to skip all 4-cent offers."}

@@

```{r General prop & earnings plots (Fig. 2), eval = !figsEnd, fig.width = 10, fig.height = 4, fig.align = "center", fig.cap = "Overall choice behavior in Experiment 1. Left: Proportion accepted per cost. Middle: Total number of dollars earned by each group by the end of the experiment. Right: The relationship between proportion accepted and total earned. Consistent with the foraging design, participants who over and under accepted earned the least. These results suggest that people were willing to pursue cognitively effortful actions at the expense of earnings."}
# plots generated in 16.2.1. and 16.1.3.
#(propPlot <- prop1 | earnings1 | earnFitplot_btw)
#ggsave("./Images/FIG2_props.png", propPlot, device = "png", height = 4, width = 10)

@@

```{r mixed effects plots (Fig. 3), eval = !figsEnd, out.width = "80%", fig.align = "center", fig.cap = "Comparison of acceptance rates across cost types for each combination of reward amount and handling time. A: Mean acceptance rate in each group for every combination of handling time and reward (with SEM). Grey points indicate the reward-maximizing acceptance rate for each combination, which was always either 0 or 1. B: Matrix of coefficients that resulted from switching the reference cost condition in a mixed-effects logistic regression model. Each element represents how much more likely a group was to accept offers compared to the reference condition (row). White asterisks denote the p-value for significant comparisons (one, two, and three askterisks correspond to p-values under 0.05, 0.01, and 0.001, respectively). C: AIC and BIC values for a mixed-effects model comparison, ranging from a baseline intercept-only model to a full-interaction model. Both metrics yielded similar values across models."}
#hrPlot_btw / (ABIC_plot_btw | ME_matrix_btw) # doesn't work with corrplot.. oh well
include_graphics("./Images/FIG3_btwlogistic.png")
```

@@

```{r Survival and prepost plots (Fig. 4), eval = !figsEnd, fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "Choice consistency and stability in Experiment 1. A: Survival curve plots of trial rejection times. B: Distributions of trial rejection times within the first 1 s of the handling time. C: Acceptance rate in the second half of the session as a function of acceptance rate in the first half of the session. Dashed lines indicate the mean for each group. D: proportion accepted over time per group."}
# individual plots generated in 16.3.1. and 16.3.2.
# to recreate the combined plot and save it:
# historyPlot_btw <- (suppressWarnings(survPlot_btw) | RTplot_btw) / (prepost_btw$scatterplot | prepost_btw$propBlocks) + 
#   plot_annotation(tag_levels = 'A') & 
#   theme(plot.tag = element_text(size = 20, face = "bold"))
# ggsave("./Images/FIG4_survivalbtw.png", historyPlot_btw, device = "png", height = 8, width = 10)
include_graphics("./Images/FIG4_survivalbtw.png")
```

@@

```{r Prepost mixed effects plot (Fig. 5), eval = !figsEnd, fig.align = "center", fig.cap = "Acceptance behavior over time in Experiment 1. A: Offer acceptance rates per handling time, reward amount, cost type, and session half, showing that effortful demands (Cognitive and Physical) were less frequently accepted over time, especially for the longest handling time (14 s). B: Mixed-effects logistic regression model coefficients denoting the comparison of acceptance rates across cost conditions for each half of the experimental session separately (mirrored along the diagonal). Even though acceptance rates decreased in the effort groups, the differences in acceptance rates across cost conditions were preserved."}
# plots in 16.3.2
# ggsave("./Images/prepost_btw.png", hrprepostPlot_btw, device = "png", height = 6, width = 6)
include_graphics("./Images/FIG5_prepostbtw.png")

@@

```{r Earnings/prop completed/ME plots (Fig. 6), eval = !figsEnd, fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "Within-subject acceptance behavior. A: Quadratic relationship between trial completions and total earnings. B: Proportion of acceptances of each reward per cost condition. C: Matrix of mixed-effects coefficients showing comparisons among cost conditions (while controlling for reward amount). Cognitive and Physical trials were compared to one another and were each compared to Wait trials from the same block (Wait-C and Wait-P, respectively). We omitted comparisons to Wait trials in the opposite block type (gray cells), which have little interpretability and were not addressed in our predictions. Asterisks mark statistically significant comparisons. D: AIC and BIC values for models of increasing complexity ("AllMain" refers to the a priori model which included main effects of cost condition and reward offer amount.)"}
# earnFitplot_wth, hrPlot_wth, mixLogis_compare_wth$plot
#ggsave("./Images/aic_wth.png", mixLogis_compare_wth$plot, device = "png", height = 5, width = 5)
include_graphics("./Images/FIG6_wthlogistic.png")
```

@@

```{r Survival and prepost plots (Fig. 7), eval = !figsEnd, fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "Choice consistency and stability in Experiment 2. A: Survival curves showing trial rejection times for each cost condition. B: Distribution of trial rejection times within the offer window. C: Acceptance rate in the last two blocks as a function of acceptance rate in the first two blocks. Dashed lines indicate the mean for each cost. D: Acceptance rates in the three successive occurrences of each block type."}
# plots generated in 16.3.1. and 16.3.3.
# historyPlot_wth <- (suppressWarnings(survPlot_wth) | suppressWarnings(RTplot_wth)) / (prepost_wth$scatterplot | prepost_wth$propBlocks) + 
#     plot_annotation(tag_levels = 'A') &
#     theme(plot.tag = element_text(size = 20, face = "bold"))
#ggsave("./Images/FIG7_survivalwth.png", historyPlot_wth, device = "png", height = 8, width = 10)
include_graphics("./Images/FIG7_survivalwth.png")
```

@@

```{r Prepost mixed effects plots (Fig. 8), eval = !figsEnd, fig.align = "center", fig.cap = "Acceptance rates over time in Experiment 2. A: Proportion accepted in the first two and last two blocks of the experiment. An initial preference for cognitive effort trials faded amid a global decrease in acceptance rates. B: Mixed effects coefficient matrix for early and late trials separately. The pattern for early trials -- but not for late trials -- resembled what was observed in Experiment 1 (Figure 3B). C: Results presented separately for participants who experienced the Cognitive/Wait block type first or who experienced the Physical/Wait block type first."}
# hrprepostPlot_wth, blockOrder_wth
# ggsave("./Images/FIG8_prepostwth.png", hrprepostPlot_wth, device = "png", height = 4, width = 8)
include_graphics("./Images/FIG8_prepostwth.png")

@@

```{r BIC and parameter comparison (Fig. 9), eval = !figsEnd, fig.align = "center", fig.height = 5, fig.width = 7, fig.cap = "Computational modeling. A: BIC values for four plausible models of choice behavior for both experiments. Lower values indicate better fit. B: Differences in cost biases produced by each demand. Negative values suggest the Cognitive group acted as if it perceived its demand as valuable. C: Parameter comparison portrays consistent foraging behavior across experiments. D: Behavior recovery of the within-subjects adaptive behavior based on the winning model. The model predictions match the initial preference for cognitive effort, and the eventual convergence of acceptances by the end of the session."}
# modelPlot <- (bicPlot + costPlot) / allFitsPlot
# ggsave("./Images/FIG9_modelresult_part.png", modelPlot, device = "png", height = 8, width = 11)
include_graphics("./Images/FIG9_modelresults.png")

@@

```{r New Task Plot (Fig. 1), eval = figsEnd, out.width = "80%", fig.align = "center", fig.cap= "Task design and optimal behavior. A: General foraging trial structure. On each trial, participants were offered an opportunity to earn money by sustaining effort or waiting during the handling time (2, 10, or 14 s). The end of a trial was followed by a travel time (handling and travel times always added up to 16 s). Participants could skip unfavorable trials and immediately start traveling to a potentially better offer. In Experiment 1, the type of demand was fixed per participant and handling time varied per block. In Experiment 2, handling time was fixed at 10 s, but a combination of effort and delay trials changed per block. B: Possible earnings per second for each acceptance threshold (i.e. the smallest amount accepted) for each handling time in Experiment 1. Circles denote the reward-maximizing threshold for each block, which is described in the table. Experiment 2 presented only the 10 s handling time, for which it was optimal to skip all 4-cent offers."}

@@

```{r New General prop & earnings plots (Fig. 2), eval = figsEnd, fig.width = 10, fig.height = 4, fig.align = "center", fig.cap = "Overall choice behavior in Experiment 1. Left: Proportion accepted per cost. Middle: Total number of dollars earned by each group by the end of the experiment. Right: The relationship between proportion accepted and total earned. Consistent with the foraging design, participants who over and under accepted earned the least. These results suggest that people were willing to pursue cognitively effortful actions at the expense of earnings."}
# plots generated in 16.2.1. and 16.1.3.
#(propPlot <- prop1 | earnings1 | earnFitplot_btw)
#ggsave("./Images/FIG2_props.png", propPlot, device = "png", height = 4, width = 10)
 prop1 | earnings1 | earnFitplot_btw
```

@@

```{r New mixed effects plots (Fig. 3), eval = figsEnd, out.width = "80%", fig.align = "center", fig.cap = "Comparison of acceptance rates across cost types for each combination of reward amount and handling time. A: Mean acceptance rate in each group for every combination of handling time and reward (with SEM). Grey points indicate the reward-maximizing acceptance rate for each combination, which was always either 0 or 1. B: Matrix of coefficients that resulted from switching the reference cost condition in a mixed-effects logistic regression model. Each element represents how much more likely a group was to accept offers compared to the reference condition (row). White asterisks denote the p-value for significant comparisons (one, two, and three askterisks correspond to p-values under 0.05, 0.01, and 0.001, respectively). C: AIC and BIC values for a mixed-effects model comparison, ranging from a baseline intercept-only model to a full-interaction model. Both metrics yielded similar values across models."}
#hrPlot_btw / (ABIC_plot_btw | ME_matrix_btw) # doesn't work with corrplot.. oh well
include_graphics("./Images/FIG3_btwlogistic.png")
```

@@

```{r New Survival and prepost plots (Fig. 4), eval = figsEnd, fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "Choice consistency and stability in Experiment 1. A: Survival curve plots of trial rejection times. B: Distributions of trial rejection times within the first 1 s of the handling time. C: Acceptance rate in the second half of the session as a function of acceptance rate in the first half of the session. Dashed lines indicate the mean for each group. D: proportion accepted over time per group."}
# individual plots generated in 16.3.1. and 16.3.2.
# to recreate the combined plot and save it:
# historyPlot_btw <- (suppressWarnings(survPlot_btw) | RTplot_btw) / (prepost_btw$scatterplot | prepost_btw$propBlocks) + 
#   plot_annotation(tag_levels = 'A') & 
#   theme(plot.tag = element_text(size = 20, face = "bold"))
# ggsave("./Images/FIG4_survivalbtw.png", historyPlot_btw, device = "png", height = 8, width = 10)
include_graphics("./Images/FIG4_survivalbtw.png")
```

@@

```{r New Prepost mixed effects plot (Fig. 5), eval = figsEnd, fig.align = "center", fig.cap = "Acceptance behavior over time in Experiment 1. A: Offer acceptance rates per handling time, reward amount, cost type, and session half, showing that effortful demands (Cognitive and Physical) were less frequently accepted over time, especially for the longest handling time (14 s). B: Mixed-effects logistic regression model coefficients denoting the comparison of acceptance rates across cost conditions for each half of the experimental session separately (mirrored along the diagonal). Even though acceptance rates decreased in the effort groups, the differences in acceptance rates across cost conditions were preserved."}
# plots in 16.3.2
# ggsave("./Images/prepost_btw.png", hrprepostPlot_btw, device = "png", height = 6, width = 6)
include_graphics("./Images/FIG5_prepostbtw.png")
```

@@

```{r New Earnings/prop completed/ME plots (Fig. 6), eval = figsEnd, fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "Within-subject acceptance behavior. A: Quadratic relationship between trial completions and total earnings. B: Proportion of acceptances of each reward per cost condition. C: Matrix of mixed-effects coefficients showing comparisons among cost conditions (while controlling for reward amount). Cognitive and Physical trials were compared to one another and were each compared to Wait trials from the same block (Wait-C and Wait-P, respectively). We omitted comparisons to Wait trials in the opposite block type (gray cells), which have little interpretability and were not addressed in our predictions. Asterisks mark statistically significant comparisons. D: AIC and BIC values for models of increasing complexity ("AllMain" refers to the a priori model which included main effects of cost condition and reward offer amount.)"}
# earnFitplot_wth, hrPlot_wth, mixLogis_compare_wth$plot
#ggsave("./Images/aic_wth.png", mixLogis_compare_wth$plot, device = "png", height = 5, width = 5)
include_graphics("./Images/FIG6_wthlogistic.png")
```

@@

```{r New Survival and prepost plots (Fig. 7), eval = figsEnd, fig.width = 8, fig.height = 7, fig.align = "center", fig.cap = "Choice consistency and stability in Experiment 2. A: Survival curves showing trial rejection times for each cost condition. B: Distribution of trial rejection times within the offer window. C: Acceptance rate in the last two blocks as a function of acceptance rate in the first two blocks. Dashed lines indicate the mean for each cost. D: Acceptance rates in the three successive occurrences of each block type."}
# plots generated in 16.3.1. and 16.3.3.
# historyPlot_wth <- (suppressWarnings(survPlot_wth) | suppressWarnings(RTplot_wth)) / (prepost_wth$scatterplot | prepost_wth$propBlocks) +
#     plot_annotation(tag_levels = 'A') &
#     theme(plot.tag = element_text(size = 20, face = "bold"))
#ggsave("./Images/FIG7_survivalwth.png", historyPlot_wth, device = "png", height = 8, width = 10)
include_graphics("./Images/FIG7_survivalwth.png")
```

@@

```{r New Prepost mixed effects plots (Fig. 8), eval = figsEnd, fig.align = "center", fig.cap = "Acceptance rates over time in Experiment 2. A: Proportion accepted in the first two and last two blocks of the experiment. An initial preference for cognitive effort trials faded amid a global decrease in acceptance rates. B: Mixed effects coefficient matrix for early and late trials separately. The pattern for early trials -- but not for late trials -- resembled what was observed in Experiment 1 (Figure 3B). C: Results presented separately for participants who experienced the Cognitive/Wait block type first or who experienced the Physical/Wait block type first."}
# hrprepostPlot_wth, blockOrder_wth
# ggsave("./Images/FIG8_prepostwth.png", hrprepostPlot_wth, device = "png", height = 4, width = 8)
include_graphics("./Images/FIG8_prepostwth.png")
```

@@

```{r New BIC and parameter comparison (Fig. 9), eval = figsEnd, fig.align = "center", fig.height = 5, fig.width = 7, fig.cap = "Computational modeling. A: BIC values for four plausible models of choice behavior for both experiments. Lower values indicate better fit. B: Differences in cost biases produced by each demand. Negative values suggest the Cognitive group acted as if it perceived its demand as valuable. C: Parameter comparison portrays consistent foraging behavior across experiments. D: Behavior recovery of the within-subjects adaptive behavior based on the winning model. The model predictions match the initial preference for cognitive effort, and the eventual convergence of acceptances by the end of the session."}
# modelPlot <- (bicPlot + costPlot) / allFitsPlot
# ggsave("./Images/FIG9_modelresult_part.png", modelPlot, device = "png", height = 8, width = 11)
include_graphics("./Images/FIG9_modelresults.png")
```
